---
title: "Trying to classify activity performance quality"
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
---
##Synopsis

This is a study of the wearable device collected data, analyzed to understand if qualitative predictions about how 'well' an excercise activity was attempted.

This paper looks at the data and come up with qualitative prediction values.

## Loading and preprocessing the data

```{r,cache=TRUE }
library(caret)
setwd("C:/Coursera/ML_Assignment")
training <- read.csv("pml-training.csv",na.strings=c("NA","NaN","#DIV/0!",""))
testing <- read.csv("pml-testing.csv",na.strings=c("NA","NaN","#DIV/0!",""))
training<-training[,colSums(is.na(training)) == 0]
testing <-testing[,colSums(is.na(testing)) == 0]


head(training)
```

## What does the data look like?

I am taking all the remaining variables other than the first 8 for the the analysis as I am not sure if escewing any variable will give us a better model.

```{r,cache=TRUE}

training   <-training[,-c(1:7)]
testing <-testing[,-c(1:7)]

```

## Divide the training data into a training set and a validation set

```{r,cache=TRUE }
Train <- createDataPartition(training$classe, p = 0.6, list = FALSE)
subTraining <- training[Train,]
subTesting <- training[-Train,]

```

## Model building

I am choosing to build a Random Forest model.

```{r,cache=TRUE }
library(caret)
library(randomForest)
model1 <- randomForest(classe ~ ., data=subTraining)

```
## Apply the model to the test data
```{r,cache=TRUE }
predTest <- predict(model1, subTesting, type = "class")

predTest
```

##Let us examine the accuracy and measure the sample for the built model

```{r,cache=TRUE }

predTrain <- predict(model1, subTraining)
confusionMatrix(predTrain, subTraining$classe)

```

